Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-05 documentation/paper.tex
Added section on hardware
Fixed slight error
Added images to show audio and image data

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}

@@

@@

@@

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{wrapfig}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{audio}
    \caption{\label{} An example of the cropped audio waveform $\omega$ and full resolution Fourier transform $\beta_{50,001}$.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{image_grid}
    \caption{\label{} An example of the image sequence $\iota$.}
\end{figure}

@@

\subsection{Hardware}

Training was done on the Graham supercomputer at the University of Waterloo, accessed through Compute Canada and SHARCNET. I would like to thank Ken Clark and SNOLAB very much for generously providing access to this hardware.
